Multi-Core Model Checking and Maximum Satisfiability Applied to Hardware-Software Partitioning

### 2016-08-09 Docs/IJES/journal.tex
updated paper version

\textcolor{red}{Conforme mencionado pelo revisor, falta definir o indice ``i''.}

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$ GB of memory.

@@

%GA
\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
& & & & & & & & & \\
\hline

@@

Finally, there are approaches that mixes heuristics with exact solution tools. The idea is to use a heuristic to speed up some phase of an exact solution tool. It worth mentioning that the final solution is not necessarily an optimal global solution. Only the SMT-based verification is guaranteed to find the exact solution, but hybrid algorithms are faster when complexity rises.

>>>>

Remembering that, as defined by formal model, there is a index of each decision variable, indicated by letter "i", which ranges from zero to the number of nodes of the problem to be solved.

%\textcolor{red}{Conforme mencionado pelo revisor, falta definir o indice ``i''.}

@@

All experiments were conducted on an otherwise idle Intel Core i$7$-$2600$ ($8$-cores), with $3$.$4$ GHz and $24$ GB of RAM, running Ubuntu $64$-bits. Each time was measured $3$ times (average taken). Based on standard deviation and tolerance interval to each set of time sample, it was obtained a statistical confidence of $91.7$\% to ESBMC (sequential, SS, PB and $\nu$Z), $95.9$\% to ESBMC-PS, and $92.0$\% to ILP and GA. A timeout condition (TO) is reached when the verification time is longer than $3600$ seconds. A memory-out (MO) occurs when the tool reaches $15$ GB of memory. The TO was defined based in previous empiric tests, where a bigger TO (5000 seconds, for example) do not caused difference in the results.

@@

%GA
\multirow{4}{*}{\textbf{\normalsize{{GA}}}}
& & & & & & & & & \\
&  \normalsize{T(s)}   &  \normalsize{6.7}   &  \normalsize{7.4}   &  \normalsize{8.8}   &  \normalsize{340.4}   &  \normalsize{2050.0}    &  \normalsize{1371.9}   &  \normalsize{TO}  \\
&  \normalsize{Hp}   &  \normalsize{17}   &  \normalsize{47}   &  \normalsize{40}   &  \normalsize{245}   &  \normalsize{647}    &  \normalsize{8619}   &  -  \\
&  \normalsize{Error \%}   &  \normalsize{13.3}   &  \normalsize{0.0}   &  \normalsize{29.0}   &  \normalsize{1.7}   &  \normalsize{-6.5}    &  \normalsize{-37.6}   &  -  \\
& & & & & & & & & \\
\hline

@@

Finally, there are approaches that mixes heuristics with exact solution tools. The idea is to use a heuristic to speed up some phase of an exact solution tool. It is worth mentioning that the final solution is not necessarily an optimal global solution. Only the SMT-based verification is guaranteed to find the exact solution, but hybrid algorithms are faster when complexity rises.
